---
geometry: margin = 1in
output:
  html_document:
    df_print: paged
---

## 3. Theory

The following chapter is intended to provide the theoretical foundations necessary for understanding our work. It is divided into a part that provides an overview of artificial neural networks. Followed by section [2.3.](#bitcoin) that shows the background and the ecosystem of Bitcoin. This knowledge should be kept in mind, which should help in understanding the price formation of Bitcoin.

### 3.1. Neural network

In the context of this work, artificial neural networks are used to answer supervised learning questions that focus on classification of data. This means that a neural network finds a correlation between the data and their labels and optimizes its parameters in order to minimize the error for the next try. This process is called supervised training and is performed with a test data sample. An application example of classification is that a neural network is used for face recognition after it has learned the classification of different faces in the process of supervised training. Predictive analysis works similarly to the classification of labeled data. It estimates future values based on past events and can be trained with historical data. On the other hand, unsupervised learning (clustering) is applied to detect patterns from unlabeled data. Based on these patterns, for example, anomalies can be detected that are relevant in the fight against fraud (fraud detection). Unsupervised learning is not discussed further in this paper.

Section [3.2.](#Perceptron) will demonstrate the functioning of a neural network using a simple perceptron.

### 3.3. Perceptron

Long-short-term-memory / Recurrent Neural Networks

### 3.3. LSTM / RNN

Long-short-term-memory / Recurrent Neural Networks

Explain.

### 3.3. Bitcoin {#bitcoin}

In this section bitcoin as a cryptocurreny is introduced. The historical data is analyzed and commentend. Further the technology in and around cryptocurrencies is briefly explained. A detailed explanation would requiere a paper itself, therefore the explanation is done as simple as possible.

In the following work bitcoin as a cryptocurreny is mentionend in its short term BTC, by the meaning of US Dollars per Bitcoin.


#### 2.3.1. historical course analysis

Bitcoin was first introduced in 2009 as the leader of a new era of cryptocurrencies. Firstly the recognition wasnt very high due to the fact of a non established technology. At the end of 2016 things began to change, more volume was flushed in the market and the price of BTC began to slowly ascend. in 2017 the real rally began and the BTC rose up to nearly 20k USD / BTC. In the following years until 2020 BTC had a lot of different phases from rising and falling to  a price at the end in 2020 around 10000 USD per BTC. Most recent events topped everything before, as the BTC rose up to 58000 US Dollar after companies like Tesla and Signal bougth in with high volume. 






```{r, echo=FALSE, message=FALSE}
# acessing data via coinmarket cap https://coinmarketcap.com/
# from yahoofinance ticker BTC-USD
# *Close price adjusted for splits.
#**Adjusted close price adjusted for both dividends and splits.

BTC_USD=getSymbols("BTC-USD",auto.assign = F) # acessing yahoo finance
BTC_USD=na.exclude(BTC_USD)                   # exclusion of nas
chartSeries(BTC_USD,type="line", theme=chartTheme("white"))
```

#### 3.3.2. SHA256 Hash

 

-   Block
-   Blockchain
-   Distributed Blockchain
-   Token
-   Coinbase Transaction
-   Public/Private Key -\> Signing
-   Signature (sign, verify)
-   Transaction

\newpage

### 3.7. Reference

#### 3.7.1. Figure Reference

 

As you can see in figure \ref{fig:fig1} -\> GOOGLE

```{r fig1, echo=FALSE, fig.cap="Visualization of the adjusted prices of the Alphabet Inc Class A Stock."}
GOOGL <- getSymbols("GOOGL", auto.assign=F)
g.adj <- GOOGL[,6]
par(mfrow=c(1,1))
plot(g.adj, main="Adjusted Prices ~ Google")
```

\newpage

#### 3.7.2. Equation Reference

 

GARCH-formula can be seen in \ref{eq:garch}

```{=tex}
\begin{align} \label{eq:garch}
  \epsilon_{t} &= \mathrm{log}(x_{t})-\mathrm{log}(x_{t-1}) \nonumber \\
  \epsilon_{t} &= \sigma_{t}u_{t} \\
  \sigma_{t}^{2} &=c \sigma^{2}+\sum_{j=1}^{n}\alpha_{j}\sigma_{t-j}^{2}+\sum_{k=1}^{m}\beta_{k}\epsilon_{t-k}^{2} \nonumber
\end{align}
```
\newpage

#### 3.7.3. Table Reference

 

In table \ref{tab:coeftable} you can see the flexerino of the coefficients.

```{r coeftable, echo=FALSE, message=FALSE}
g.adj.lr <- na.exclude(diff(log(g.adj)))
g.subset.lr <- head(g.adj.lr, length(g.adj.lr)-100)
y.garch_11 <- garchFit(~garch(1,1), data=g.subset.lr, delta=2, include.delta=F, 
                       include.mean=F, trace=F)
r1 <- y.garch_11@fit$matcoef[,1]
r2 <- y.garch_11@fit$matcoef[,2]
r3 <- y.garch_11@fit$matcoef[,4]
paras <- data.frame(r1, r2, r3)
rownames(paras) <- c("$\\omega$", "$\\alpha_{1}$", "$\\beta_{1}$")
colnames(paras) <- c("Estimate", "Std. Error", "p-Value")
kable(paras, "latex", escape=F, booktabs = T, linesep="", caption="Coefficients GARCH(1,1).", digits=20)
```

\newpage

#### 3.7.4. Section Reference {#sec-ref}

Here we can see a wild section, which will reference to itself: [2.7.4.](#sec-ref)

Or reference to the Bitcoin-section [2.3.](#bitcoin)

\newpage

#### 3.7.5. Literature Reference

Add bibliography reference in the `.bib`-file in the add folder.

Here I make a reference to the original bitcoinpaper [@bitcoin] `[@bitcoin]` or to the specific page on the NN financial trading paper [@nnfin, pp. 6-8] -\> `[@nnfin, pp. 6-8]`
